### 2017-04-06 paper/evaluation.tex
pass on rq6

@@

To answer \numRQF{}, we considered the top ten projects with
long-running test suites and all parallel modes (see
Section~\ref{sec:modes}). In this experiment, we run the test suites
with different parallel modes and evaluated the average time cost and
rate of failing tests. To avoid noise, we carefully selected only
subjects with nonfailing tests to avoid noise in our measurements.

@@

\subsubsection{Trade-offs}
\label{seq:rq6-tradeoffs}
\Fix{discuss trade-offs and elaborate conclusion....}

>>>>

\subsection{Tradeoffs}
\label{sec:rq6-tradeoffs}

This dimension assesses the impact of using distinct parallel
configurations on test flakiness (negative impact) and speedup
(positive impact).  Recall that increased resource contention obtained
with parallelism can lead to concurrency issues such as data races.
Hence, flakiness and speedup are contradictory forces that drive
configuration selection.  Note also that Section~\ref{sec:rqD}
evaluated variable speedup in isolation, focused on project
configuration where parallelism is used by default.

@@

To answer this research question we selected projects as follows.  To
avoid noise in our measurements, we first discarded projects
containing failing tests (note that we measure flakiness).  Then, we
sorted projects in descending order of their execution times and
selected the top ten projects from the resulting set.

In this experiment, the baseline technique is \Seq{} and the
evaluation techniques are all the configuration modes listed in
Section~\ref{sec:modes}.  We ran each of the technique for \Fix{X}
times reporting elapsed time and number of failing tests each time.
We reported average results.

@@
